Proportional multi-state multiple-cohort life table model

### 2018-04-10 MSLT/MSLTdoc.Rmd
Plot mortality rates males

mx_plot_compare <- ggplot(data = filter(GBDEngland, sex == "male", cause == "all causes" & measure == "deaths") %>% select(measure, location, sex, age, metric, cause, one_rate, age_cat), aes(x = age_cat)) +
    geom_line(mapping = aes(y = one_rate, colour = "one_rate")) +
  theme_classic()

#Print to view
print(mx_plot_compare)

>>>>

##Select data from data frames for all cause mortality males

ggplot_data_England <- filter(GBDEngland, sex == "male", cause == "all causes" & measure == "deaths") %>% select(measure, location, sex, age, metric, cause, one_rate, age_cat)

ggplot_data_GL <- filter(GBDGL, sex == "male", cause == "all causes" & measure == "deaths") %>% select(measure, location, sex, age, metric, cause, one_rate, age_cat)

##Plot all cause mortality rates males 
mx_plot_compare_male <- ggplot() + 
geom_line(data=ggplot_data_England, aes(x= age_cat, y= one_rate), color='green') +
geom_line(data=ggplot_data_GL, aes(x= age_cat, y= one_rate), color='red') +
xlab ("Age") + ylab ("Rate per one") + labs (title = "Mortality rates comparison") +
theme_classic() +
scale_alpha_manual("Location", values = c("England", "Greater London")) +

#Print to view
print(mx_plot_compare_male)
